The serious gap laying on healthcare system in Thailand^[Code and data are available at: https://github.com/SANGWOONG-LEE/Thailand_Healthcare]

### 2022-04-05 outputs/paper/paper.Rmd
reference fix

# References
https://www.statista.com/statistics/455942/urbanization-in-thailand/
https://www.statista.com/statistics/269967/urbanization-in-the-united-states/
“Primary Health Care Systems (PRIMASYS).” Accessed April 4, 2022. https://www.who.int/alliance-hpsr/projects/alliancehpsr_thailandprimasys.pdf.

>>>>

# References
O'Neill, Aaron. “Thailand - Urbanization 2010-2020.” Statista, February 2, 2022. https://www.statista.com/statistics/455942/urbanization-in-thailand/.

O'Neill, Aaron. “United States - Urbanization 2020.” Statista, February 2, 2022. https://www.statista.com/statistics/269967/urbanization-in-the-united-states/.

“Primary Health Care Systems (PRIMASYS).” Accessed April 4, 2022. https://www.who.int/alliance-hpsr/projects/alliancehpsr_thailandprimasys.pdf.
